---
title: "Team Troubleshooting Deliverable 2"
output: github_document
---

```{r include = FALSE}
knitr::opts_chunk$set(error = TRUE)
```
0
There are **11 code chunks with errors** in this Rmd. Your objective is to fix all of the errors in this worksheet. For the purpose of grading, each erroneous code chunk is equally weighted.

Note that errors are not all syntactic (i.e., broken code)! Some are logical errors as well (i.e. code that does not do what it was intended to do).

## Exercise 1: Exploring with `select()` and `filter()`

[MovieLens](https://dl.acm.org/doi/10.1145/2827872) are a series of datasets widely used in education, that describe movie ratings from the MovieLens [website](https://movielens.org/). There are several MovieLens datasets, collected by the [GroupLens Research Project](https://grouplens.org/datasets/movielens/) at the University of Minnesota. Here, we load the MovieLens 100K dataset from Rafael Irizarry and Amy Gill's R package, [dslabs](https://cran.r-project.org/web/packages/dslabs/dslabs.pdf), which contains datasets useful for data analysis practice, homework, and projects in data science courses and workshops. We'll also load other required packages.

```{r}
### ERROR HERE ###

#load.packages(dslabs)
#load.packages(tidyverse)
#load.packages(stringr)
#install.packages("devtools") # Do not run this if you already have this package installed! 
#devtools::install_github("JoeyBernhardt/singer")
#load.packages(gapminder)

###ASSIGNED TO: Maggie

### ISSUE: incorrect usage of the load.packages function. This function is not a standard function in R, and it's not used to load packages. Instead, we should use the library function to load packages in R.

### SOLUTION: Replace load.packages() with the library() function.

### CORRECT CODE ###

##install.packages("dslabs")
  #note: I did not have the "dslabs" package; first, install the package! but don't keep this line in your code

#install.packages("devtools") 
    # Do not run this if you already have this package installed! 
    #I had to run this code because I did not have the package

library(dslabs)
library(tidyverse)
library(stringr)
library(devtools)
library(gapminder)
devtools::install_github("JoeyBernhardt/singer")




```



Let's have a look at the dataset! My goal is to:

-   Find out the "class" of the dataset.
-   If it isn't a tibble already, coerce it into a tibble and store it in the variable "movieLens".
-   Have a quick look at the tibble, using a *dplyr function*.

```{r}
### ERROR HERE ###

#class(dslabs::movielens)
#movieLens <- as_tibble(dslabs::movielens)
#dim(movieLens)

###ASSIGNED TO: Keren

### ISSUE: as_tibble function is not available in the dslabs package. To convert the dataset to a tibble, we can use the as_tibble function from the tibble package, which is part of the tidyverse. 

### SOLUTION: We need to call the "tibble" library. 

### CORRECT CODE ###

library(tibble)

class(dslabs::movielens)
movieLens <- as_tibble(dslabs::movielens)
dim(movieLens)

#look at the tibble
head(movieLens)
```

Now that we've had a quick look at the dataset, it would be interesting to explore the rows (observations) in some more detail. I'd like to consider the movie entries that...

-   belong *exclusively* to the genre *"Drama"*;
-   don't belong *exclusively* to the genre *"Drama"*;
-   were filmed *after* the year 2000;
-   were filmed in 1999 *or* 2000;
-   have *more than* 4.5 stars, and were filmed *before* 1995.

```{r}
### ERROR HERE ###

#filter(movieLens, genres == "Drama") 
#filter(movieLens, !genres == "Drama") 
#filter(movieLens, year >= 2000)
#filter(movieLens, year == 1999 | month == 2000) 
#filter(movieLens, rating > 4.5, year < 1995)


###ASSIGNED TO: Maggie

### ISSUE: 
# (1) The third line of code above looking for movies filmed *after* the year 2000 is incorrect as it currently filters movie entries in 2000 or after (>=), not just after 2000 (>). 
# (2) The fourth line of code above looking for movies filmed in 1999 *or* 2000 is incorrect because when you run the code it indicates the object "month" is not found; we should be using the c() function instead. 

### SOLUTION: For issue (1), change >= into > in third line of code. For issue (2), use the following: "year %in% c(1999, 2000)" to look for movies that were filmed in 1999 OR 2000.

### CORRECT CODE ###
#belong *exclusively* to the genre *"Drama"* [original code was correct]
filter(movieLens, genres == "Drama") 

#don't belong *exclusively* to the genre *"Drama"* [original code was correct]
filter(movieLens, !genres == "Drama") 

#were filmed *after* the year 2000 [original code was INCORRECT]
filter(movieLens, year > 2000) 

#were filmed in 1999 *or* 2000 [original code was INCORRECT]
filter(movieLens, year %in% c(1999, 2000)) 
#alternative coding: filter(movieLens, year == 1999 | year == 2000)

#have *more than* 4.5 stars, and were filmed *before* 1995 [original code was correct]
filter(movieLens, rating > 4.5, year < 1995) 
```



While filtering for *all movies that do not belong to the genre drama* above, I noticed something interesting. I want to filter for the same thing again, this time selecting variables **title and genres first,** and then *everything else*. But I want to do this in a robust way, so that (for example) if I end up changing `movieLens` to contain more or less columns some time in the future, the code will still work. Hint: there is a function to select "everything else"...

```{r}
### ERROR HERE ###

#movieLens %>%
#  filter(!genres == "Drama") %>%
#  select(title, genres, year, rating, timestamp)

###ASSIGNED TO: Edison

### ISSUE: The code syntax is fine. However, we need to select title and genres and everything else even if we change the dataset. 

### SOLUTION: We need to nest the everything function in the select function

### CORRECT CODE ###
movieLens %>%
  filter(!genres == "Drama") %>%
  select(title, genres, everything()) #is this right? even if I change the dataset? SOMEONE DOUBLE CHECK!!
```


## Exercise 2: Calculating with `mutate()`-like functions

Some of the variables in the `movieLens` dataset are in *camelCase* (in fact, *movieLens* is in camelCase). Let's clean these two variables to use *snake_case* instead, and assign our post-rename object back to "movieLens".

```{r}
### ERROR HERE ###
#movieLens <- movieLens %>%
#  rename(user_id == userId,
#         movie_id == movieId)

###ASSIGNED TO: Keren

### ISSUE: #The error is due to the incorrect syntax in the rename function. We are using the == operator, which is not valid for renaming columns.

### SOLUTION: correct the equal operation sign 

### CORRECT CODE ###
movieLens <- movieLens %>%
  rename(user_id = userId,
  movie_id = movieId) 

```

As you already know, `mutate()` defines and inserts new variables into a tibble. There is *another mystery function similar to `mutate()`* that adds the new variable, but also drops existing ones. I wanted to create an `average_rating` column that takes the `mean(rating)` across all entries, and I only want to see that variable (i.e drop all others!) but I forgot what that mystery function is. Can you remember?

```{r}
### ERROR HERE ### 

#mutate(movieLens,
#       average_rating = mean(rating))

###ASSIGNED TO: Keren 

### ISSUE: The function is called transmute() in R. transmute() is similar to mutate(), but it creates new variables and drops all existing ones except for the ones you explicitly specify. 

### SOLUTION: Change mutate to transmute.

### CORRECT CODE ###
transmute(movieLens,
       average_rating = mean(rating))

```

## Exercise 3: Calculating with `summarise()`-like functions

Alone, `tally()` is a short form of `summarise()`. `count()` is short-hand for `group_by()` and `tally()`.

Each entry of the movieLens table corresponds to a movie rating by a user. Therefore, if more than one user rated the same movie, there will be several entries for the same movie. I want to find out how many times each movie has been reviewed, or in other words, how many times each movie title appears in the dataset.

```{r}
movieLens %>%
  group_by(title) %>%
  tally()

#The above code is correct for finding out how many times each movie has been reviewed in the "movieLens" dataset. It uses the group_by() function to group the data by the "title" column and then applies the tally() function to count the number of rows (reviews) within each group (movie title).
```

Without using `group_by()`, I want to find out how many movie reviews there have been for each year.

```{r}
### ERROR HERE ###
#movieLens %>%
#  tally(year)

###ASSIGNED TO: Keren

### ISSUE: To find out how many movie reviews there have been for each year without using group_by(), we can directly use count() on the "year" column.

### SOLUTION: Directly use count() on the "year" column.

### CORRECT CODE ###
movieLens %>%

  count(year)
```


Both `count()` and `tally()` can be grouped by multiple columns. Below, I want to count the number of movie reviews by title and rating, and sort the results.

```{r}
### ERROR HERE ###
#movieLens %>%
#  count(c(title, rating), sort = TRUE)

###ASSIGNED TO: Jacky

### ISSUE: The error in  code is due to the incorrect use of count(). When we want to count by multiple columns and sort the results, we should pass those columns as separate arguments to the count() function, not as a single vector. 


### SOLUTION: Count columns as separate arguments

### CORRECT CODE ###
movieLens %>%
  count(title, rating, sort = TRUE)

```

Not only do `count()` and `tally()` quickly allow you to count items within your dataset, `add_tally()` and `add_count()` are handy shortcuts that add an additional columns to your tibble, rather than collapsing each group.

## Exercise 4: Calculating with `group_by()`

We can calculate the mean rating by year, and store it in a new column called `avg_rating`:

```{r}
movieLens %>%
  group_by(year) %>%
  summarize(avg_rating = mean(rating))

#no error in this code!
```

Using `summarize()`, we can find the minimum and the maximum rating by title, stored under columns named `min_rating`, and `max_rating`, respectively.

```{r}
### ERROR HERE ###
#movieLens %>%
#  mutate(min_rating = min(rating), 
#         max_rating = max(rating))

###ASSIGNED TO: Jacky

### ISSUE: we need to use the summarize function instead of the mutate function

### SOLUTION: 

### CORRECT CODE ###
movieLens %>%
group_by(title) %>%

  summarize(min_rating = min(rating), 
         max_rating = max(rating))


```

## Exercise 5: Scoped variants with `across()`

`across()` is a newer dplyr function (`dplyr` 1.0.0) that allows you to apply a transformation to multiple variables selected with the `select()` and `rename()` syntax. For this section, we will use the `starwars` dataset, which is built into R. First, let's transform it into a tibble and store it under the variable `starWars`.

```{r}
starWars <- as_tibble(starwars)
#this code is correct!


```

We can find the mean for all columns that are numeric, ignoring the missing values:

```{r}
starWars %>%
  summarise(across(where(is.numeric), function(x) mean(x, na.rm=TRUE)))
 #this code is correct!

```

We can find the minimum height and mass within each species, ignoring the missing values: 



```{r}
### ERROR HERE ###
#starWars %>%

#  group_by(species) %>%
#  summarise(across("height", "mass", function(x) min(x, na.rm=TRUE)))


###ASSIGNED TO: Edison

### ISSUE: The error in this code is due to the incorrect use of across(). When we want to apply a function to multiple columns, we should provide a selection specification, which can be a range of columns or column names. In the above code, we're trying to use "height" and "mass" as arguments to across(), which is not the correct way to specify multiple columns.

### SOLUTION: 

### CORRECT CODE ###
starWars %>%
  group_by(species) %>%
  summarise(across(c("height", "mass"), ~min(., na.rm = TRUE), .names = "min_{.col}"))

```





Note that here R has taken the convention that the minimum value of a set of `NA`s is `Inf`.

## Exercise 6: Making tibbles

Manually create a tibble with 4 columns:

-   `birth_year` should contain years 1998 to 2005 (inclusive);
-   `birth_weight` should take the `birth_year` column, subtract 1995, and multiply by 0.45;
-   `birth_location` should contain three locations (Liverpool, Seattle, and New York).

```{r}
### ERROR HERE ###

#fakeStarWars <- tribble(
#  ~name,            ~birth_weight,  ~birth_year, ~birth_location
#  "Luke Skywalker",  1.35      ,   1998        ,  Liverpool, England,
#  "C-3PO"         ,  1.80      ,   1999        ,  Liverpool, England,
#  "R2-D2"         ,  2.25      ,   2000        ,  Seattle, WA,
#  "Darth Vader"   ,  2.70      ,   2001        ,  Liverpool, England,
#  "Leia Organa"   ,  3.15      ,   2002        ,  New York, NY,
#  "Owen Lars"     ,  3.60      ,   2003        ,  Seattle, WA,
#  "Beru Whitesun Iars", 4.05   ,   2004        ,  Liverpool, England,
#  "R5-D4"         ,  4.50      ,   2005        ,  New York, NY,
#)


###ASSIGNED TO: Kiana

### ISSUE: There is a syntax error in your code when specifying the birth_location column. 

### SOLUTION: You should use double quotes to enclose location names that contain spaces. 

### CORRECT CODE ###
fakeStarWars <- tribble(
  ~name,           ~birth_year, ~birth_weight, ~birth_location,
  "Luke Skywalker", 1998, (1998 - 1995) * 0.45, "Liverpool, England",
  "C-3PO",          1999, (1999 - 1995) * 0.45, "Liverpool, England",
  "R2-D2",          2000, (2000 - 1995) * 0.45, "Seattle, WA",
  "Darth Vader",    2001, (2001 - 1995) * 0.45, "Liverpool, England",
  "Leia Organa",    2002, (2002 - 1995) * 0.45, "New York, NY",
  "Owen Lars",      2003, (2003 - 1995) * 0.45, "Seattle, WA",
  "Beru Whitesun Iars", 2004, (2004 - 1995) * 0.45, "Liverpool, England",
  "R5-D4",          2005, (2005 - 1995) * 0.45, "New York, NY"
)


```

## Attributions

Thanks to Icíar Fernández-Boyano for writing most of this document, and Albina Gibadullina, Diana Lin, Yulia Egorova, and Vincenzo Coia for their edits.
